\cvsection{Experience}
\begin{cventries}
   	\cventry
    {Programmer Analyst}
    {First Hawaiian Bank}
    {Honolulu, HI}
    {Nov 2016 - present}
    {
        \begin{cvitems}
            \item {Maintained and extended a complex legacy application used by bank tellers, with attention to the quality assurance of released code.}
            \item {Resolved various production issues/bugs in a timely manner, maintaining a high satisfaction score.}
            \item {Maintained numerous servers using Python, Perl and Batch scripts.}
            \item {Successfully collaborated with a sizable IT team to deliver a major project.}
            \item {Fixed a long queue of unresolved software issues, some over four years old.}
        \end{cvitems}
    }

	\cventry
	{Web and Database Developer}
	{Curriculum Research and Development Group, University of Hawai`i at M{\char"101}noa}
	{Honolulu, HI}
	{Apr 2016 - present}
	{
		\begin{cvitems}
			\item {Designed and developed opihi.crdg.hawaii.edu using the Zend php framework, applying best security practices and promoting accessibility of the website for handicap users. Opihi is a research project relying on data gathered by public to study the intertidal regions of Hawaii}
			%\item {Worked with non-technical clients to define software requirements and design an ideal look and feel for the website.}
			\item {Used D3.js to create beautiful and responsive graphs for analyzing scientific data collected by students.}
		\end{cvitems}
	}

%	\cventry
%	{Website Administrator}
%	{First Unitarian Church of Hawaii}
%	{Honolulu, HI}
%	{Jan 2018 - present}
%	{
%	\begin{cvitems}
%		\item {This is volunteer position. I upkeep, troubleshoot, and extend the functionality of a wordpress based website for the First Unitarian Church of Hawaii.}
%	\end{cvitems}
%	}

	\cventry
	{Front End Developer}
	{University of Hawai`i at M{\char"101}noa}
	{Honolulu, HI}
	{Oct 2016 - Mar 2017}
	{
		\begin{cvitems}
			\item {Worked with Professor Kaveh Abhari to create a vibrant data-analysis page for Stemd2.com (an educational website).}
			\item {Developed a preliminary front-end framework to include multiple data-enabled widgets on the page.}
			%\item {Reverse-engineered a sophisticated word-press plugin and wrote custom php code to extend its functionality.}
			%\item {Helped eight struggling students improve their grades and pass the class.}
		\end{cvitems}
	}

    \cventry
    {Web Developer}
    {Hasti LLC}
    {Honolulu, HI}
    {June 2016 - Nov 2016}
    {
        \begin{cvitems}
            \item {Developed a web application for AASHTO LRFD (i.e. bridge design) calculations with Node and Angular(\textbf{\href{http://www.aashtobridgedesign.com}{aashtobridgedesign.com}})}
        \end{cvitems}
    }

    % \cventry
    % {IT Support}
    % {Kai Hawaii Structural and Forensic Engineers}
    % {Honolulu, HI}
    % {September 2016 - Nov 2016}
    % {
	%     \begin{cvitems}
	% 	    \item{Provided general technical assistance to engineers. Performed regular server maintenance duties.}
	% 	    \item{Worked to debug internal programs including onboard logic for a survey robot.}
	%     \end{cvitems}	
    % }
	
	\cventry
	{Directed Studies Under Dr. Vahsen}
	{Department of Physics University of Hawai`i at M{\char"101}noa}
	{Honolulu, HI}
	{2013}
	{
		\begin{cvitems}
			\item {Developed an application to select, display and graph neutron trajectories identified by a neutron detector using C++ and
				ROOT under the guidance of Professor Sven Vahsen.}
		\end{cvitems}
	}

	\cventry
	{Undergraduate Research Assistant}
	{Department of Molecular Biosciences, University of Hawai`i at M{\char"101}noa}
	{Honolulu, HI}
	{2011-2013}
	{
		\begin{cvitems}
			\item{Contributed to a two year long bioinfomatics research project and won an award for presenting the project at a research symposium.}
			\item {Created a database of retro-transposons present in the corn genome using MySQL and Perl.}
			\item {Created a website to allow public access to the database using PHP and Apache.}
			%\item {Helped eight struggling students improve their grades and pass the class.}
		\end{cvitems}
	}

\end{cventries}

