%some fa icons to use: faAndroid faDesktop faChrome faLaptop faWrench faTrophy
\cvsection{Projects}

	Please find links and detailed description of my projects on my portfolio at \mbox{\href{http://www.tpourjalali.com}{www.tpourjalali.com}}.
\begin{cventries}
	
	\cventry
	{\faLaptop\faAndroid\enspace Developer Portfolio}
	{}
	{}
	{}
	{My developer pages (at \textbf{\href{http://www.tpourjalali.com}{tpourjalali.com}} and \textbf{\href{https://tahahojati.github.io}{ tahahojati.github.io}}) were developed using Vue.js, Angular.js and Android SDK.}

	\cventry
	{\faLaptop \enspace OPIHI: Our Project in Hawaii's Intertidal Region}
	{}
	{}
	{}
	{A science education web application, developed with Zend Framework and LAMP stack}
	
	\cventry
	{\faAndroid\enspace Reflex Game}
	{}
	{}
	{}
	{A fast paced game developed using only Android SDK. APK available for download on my \textbf{\href{https://github.com/tahahojati/ReflexGame}{github}} and on my portfolio.}

	\cventry
	{\faLaptop\enspace AASHTO LRFD DESIGN Online Software}
	{}
	{}
	{}
	{Web app for performing structural engineering calculations and generating pdf reports. Developed with Express and Angular. }
	
	
	\cventry
	{\faAndroid\enspace Poppin' Movies}
	{}
	{}
	{}
	{Android app that shows popular movies along with trailers and reviews.  Users may rate and share the movies as they like. }
	
	% \cventry
	% {\faAndroid\enspace Criminal Intent}
	% {}
	% {}
	% {}
	% {Co-workers leaving dirty dishes in the breakroom sink? leaving shared printer without paper? Record their crimes using this app!}

	% \cventry
	% {\faAndroid\enspace Vue Stock Trader}
	% {}
	% {}
	% {}
	% {}
	
	% \cventry
	% {\faAndroid\enspace Be Happy}
	% {}
	% {}
	% {}
	% {}
	
	\cventry
	{\faTrophy\faAndroid\enspace Farm Akamai}
	{}
	{}
	{}
	{Winner in Hawaii Agriculture Hackathon 2018. An Android app to educate ESL immigrants about Hawaii's standards of farming.}

%virtual pet, farm animals, frogger
	\cventry
	{\faChrome\enspace JavaScript Games}
	{}
	{}
	{}
	{Set of browser games developed with vanilla JavaScript and with Phaser.io. Look for them on my online portflio.}
	
	\cventry
	{\faAndroid \faLaptop\enspace Ristorante con Fusion
	}
	{}
	{}
	{}
	{Single page application accompanied by a hybrid mobile app for a fictitious restaurant. Developed with Express, Angular and Ionic.}

	\cventry
	{\faAndroid\enspace Sandwich Club}
	{}
	{}
	{}
	{An Android app to help one find and prepare sandwiches}
			
	% \cventry
	% {\faAndroid\enspace Portfolio}
	% {}
	% {}
	% {}
	% {}
	

	
	\cventry
	{\faAndroid\enspace Photo Gallery}
	{}
	{}
	{}
	{An Android client for the photo-sharing site Flickr.}
	
	\cventry
	{\faAndroid\enspace Beat Box}
	{}
	{}
	{}
	{An Android app for generating musical sounds.}
		
	% \cventry
	% {\faAndroid\enspace Nerd Launcher}
	% {}
	% {}
	% {}
	% {A simple app to replace the default Android Launcher (Home screen)}
		
	% \cventry
	% {\faAndroid\enspace Geo Quiz}
	% {}
	% {}
	% {}
	% {}
		
	% \cventry
	% {\faAndroid\enspace Sunset}
	% {}
	% {}
	% {}
	% {}
		
	% \cventry
	% {\faLaptop\enspace Coffee in Honolulu}
	% {}
	% {}
	% {}
	% {A map of coffee shops in Honolulu developed using Knockout.js framework and Google Maps and FourSquare APIs.}

	% \cventry
	% {\faLaptop\enspace Frogger
	% }
	% {}
	% {}
	% {}
	% {A JavaScript version of the classic arcade game Frogger. Developed with pure vanilla JavaScript.}


\end{cventries}
