\cvsection{Experience}
\begin{cventries}
	\cventry
	{Web and Database Developer}
	{Curriculum Research and Development Group at University of Hawai`i at M{\char"101}noa}
	{Honolulu, HI}
	{Apr 2016 - present}
	{
		\begin{cvitems}
			\item {Software developer for the OPIHI project.}
		\end{cvitems}
	}
    \cventry
    {Web Developer}
    {Hasti LLC}
    {Honolulu, HI}
    {June 2016 - present}
    {
        \begin{cvitems}
            \item {Software developer for the AASHTO LRFD project.}
        \end{cvitems}
    }
    \cventry
    {IT Assistant}
    {Kai Hawaii Structural and Forensic Engineers}
    {Honolulu, HI}
    {September 2016 - present}
    {
	    \begin{cvitems}
		    \item{Provide general technical assistance to engineers. Perform regular server maintenance duties.}	
	    \end{cvitems}	
    }
	
	\cventry
	{Physics Tutor}
	{University of Hawai`i at M{\char"101}noa}
	{Honolulu, HI}
	{2014}
	{
		\begin{cvitems}
			\item {Worked closely with students to deepen their knowledge of physics.}
			%\item {Helped eight struggling students improve their grades and pass the class.}
		\end{cvitems}
	}
	\cventry
	{Directed Studies Under Dr. Vahsen}
	{Department of Physics University of Hawai`i at M{\char"101}noa}
	{Honolulu, HI}
	{2013}
	{
		\begin{cvitems}
			\item {Devised an app with graphical user interface to select, display, and graph neutron trajectories identified by a neutron detector using C++ and
				ROOT under the guidance of Dr. Sven Vahsen.}
		\end{cvitems}
	}
	\cventry
	{Department of Molecular Biosciences and Bioengineering at University of Hawai`i at M{\char"101}noa}
	{Undergraduate Research Assistant}
	{Honolulu, HI}
	{2011-2013}
	{
		\begin{cvitems}
			\item {Created a database of retro-transposons in Corn genome using MySQL and Perl.}
			\item {Created a website to expose the database to public using PHP5 and Appache2.}
			%\item {Helped eight struggling students improve their grades and pass the class.}
		\end{cvitems}
	}
\end{cventries}

